Paper Title

### 2020-10-10 Paper/investigating-effectiveness.tex
added FCE Parser

\cite{lu2020investigating} uses an evaluation based on 8 datasets from different domains
to show that transformer-based language models consistently outperform more commonly used 
vector representations like word embeddings or bag-of-words.

>>>>

\cite{lu2020investigating} uses an evaluation based on 8 datasets from different domains
to show that transformer-based language models consistently outperform more commonly used 
vector representations like word embeddings or bag-of-words. Comparing to BERT-like models, 
representations based on Roberta produce the best results. Additionally, averaged word 
representations are the most effective as compared to CLS tokens. An Adaptive Tuning 
Active Learning (ATAL) algorithm is proposed where labelled information is utilized for 
improving effectiveness of embeddings other than training classifiers.
